Knowledge Representation for Service Robots: A Survey

### 2014-04-16 krs-survey.tex
Fixed cite, redundant table,...

\title{Knowledge Representation for Service Robots: Supply and Demand}
\author{Séverin Lemaignan, Moritz Tenorth, Michael Beetz, Rachid Alami}

@@

\tikzstyle {taxonomy} = [grow=right, level distance = 3cm, sibling
distance=7mm]
\tikzstyle {completetaxonomy} = [grow=right]
\tikzstyle {taxon} = [text width=3cm, text centered,inner sep=0pt, outer
sep=2pt] %, draw=blue!50,thick]

\maketitle
\tableofcontents

@@

Besides, we have decided to restraint the set of systems to those actually
implemented on robots, and used in semantic-rich environments (\ie dynamic,
partially unknown environments with a large range of different entities which
may have interactions). The typical scenario that would involve such robots is
a service robot in a human-friendly environment like a kitchen (we will
describe such a scenario in section~\ref{sect|scenario}).

@@

We have also chosen not to include the GOLOG language and its
derivatives~\cite{Levesque1997, Ferrein2008, Gspandl2011} in this survey. While
several implementations on robots, including service robots, do exist, the
focus of this language is on representation and reasoning about actions and
situations, and the link with symbolic, abstract knowledge is not explicit.

@@

The next paragraph details only briefly the exact meaning of these categories
and introduce accordingly sub-categories. We kindly refer the interested reader
to~\cite{blabla} for in-depth discussion of each of these dimensions of
knowledge representation systems, as well as related literature.

@@

This category focuses on questions that involve
representational challenges (time, space, context) or require specific
cognitive capabilities (theory of mind, introspection, memory).
Note that the general strategies to actually \emph{construct} a
knowledge model are treated in section~\ref{sect|design-strategies}.

@@

Again, the descriptions of these ten subcategories hereafter are very
superficial. Readers can refer to~\cite{blabla} for the details.

@@

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}p{2.4cm}p{3.4cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & Main reference \\
\midrule
ARMAR/Tapas & Formal & Holzapfel, Waibel \par (Karlsruhe TH) & & TFS (Typed Feature Structures) & \cite{Holzapfel2008}\\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ.,
DFKI Saarbrücken) & & Amodal proxies & \cite{Jacobsson2008} \\
GSM & Structural & Mavridis, Roy \par (MIT MediaLab) & & & \cite{Mavridis2006} \\
Ke Jia Project & Formal & Chen et al. \par (Univ. of Science and Technology of China) & ASP (Answer Set Programming) & ASP & \cite{Chen2010} \\
{\sc KnowRob} & Formal & Tenorth, Beetz \par (TU Munich) & {\sc Prolog} & {\sc Prolog} + OWL-DL &  \cite{Tenorth2009a} \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & NKRL & & \cite{Sabri2011} \\
%OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
ORO & Formal & Lemaignan, Alami \par (LAAS-CNRS) & {\sc Java} & OWL-DL ({\sc Jena}) + {\sc Pellet} & \cite{Lemaignan2010} \\
OUR-K/OMRKF & Formal & Lim, Suh et al. \par (Hanyang Univ.) & ? & DL + Horn Clauses &  \cite{Lim2011, Suh2007} \\
PEIS KR\&R & Formal & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & \cite{Daoutis2009} \\
%Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

CAS (\emph{CoSy Architecture Schema}) Toolkit~\cite{Hawes2007} is a
comprehensive toolkit aimed at building cognitive architectures for robots
through a set of interconnected \emph{SA} (\emph{subarchitectures}). The CAS
does not expose a central knowledge base as seen in other works. It represents
instead knowledge as unrooted \emph{proxies}. Those proxies are formally
defined in \cite{Jacobsson2008} as $p= \langle F_p, u_p \rangle$ where $F_p$ is
a set of instantiated features (like $\phi^{Colour}_{red}$) and $u_p$ a
\emph{proxies union} that form an equivalence class corresponding to one
entity.

@@

\begin{tabular}{ll}
\toprule
{\bf Project} & {\bf Common-sense knowledge source} \\
\midrule
ARMAR/{\sc Tapas} & Custom ontology related to the kitchen\\
CAST Proxies &  None \\
GSM &  Predefined categories \\
Ke Jia & None \\
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology, physics simulation \\
NKLR &  None \\
OUR-K & {\it A priori} knowledge structure and axioms, custom set of instances\\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\

@@

\end{tabular}
\end{center}
\caption{Underlying common-sense knowledge sources for each project.}
\label{table|knowledge-sources}
\end{table}

@@

Learning at the level of the knowledge representation system has been explored
in conjunction with visual perception systems (mentioned for instance, in the
CAST project, in~\cite{Jakobsson2008}). {\sc KnowRob}, by filling its pool of
facts from informations automatically extracted from the Web~\ref{Nyga2009},
can also be considered as a \emph{learning} system (it autonomously acquire
knowledge). We lack however a formal study of learning strategies and
techniques at the knowledge representation level.

>>>>

\title{Knowledge Representation for Service Robots: A Survey}
\author{Séverin Lemaignan, Moritz Tenorth, Rachid Alami, Michael Beetz}

@@

\maketitle

@@

Besides, we have decided to restraint the set of systems to those actually
implemented on robots, and used in semantic-rich environments (\ie dynamic,
partially unknown environments with a large range of different entities which
may have interactions). The typical scenario that would involve such robots is
a service robot in a human-friendly environment like a kitchen.

@@

We have also chosen not to include the GOLOG language and its
derivatives~\cite{levesque1997golog, Ferrein2008, Gspandl2011} in this survey. While
several implementations on robots, including service robots, do exist, the
focus of this language is on representation and reasoning about actions and
situations, and the link with symbolic, abstract knowledge is not explicit.

@@

The next paragraph details only briefly the exact meaning of these categories
and introduce accordingly sub-categories. We kindly refer the interested reader
to~\cite{lemaignan2012symbolic} for in-depth discussion of each of these
dimensions of knowledge representation systems, as well as related literature.

@@

This category focuses on questions that involve
representational challenges (time, space, context) or require specific
cognitive capabilities (theory of mind, introspection, memory).

@@

Again, the descriptions of these ten subcategories hereafter are very
superficial. Readers can refer to~\cite{lemaignan2012symbolic} for the details.

@@

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}p{2.4cm}p{3.4cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & Main reference \\
\midrule
ARMAR/Tapas & Formal & Holzapfel, Waibel \par (Karlsruhe TH) & & TFS (Typed Feature Structures) & \cite{Holzapfel2008}\\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ.,
DFKI Saarbrücken) & & Amodal proxies & \cite{jacobsson2008crossmodal} \\
GSM & Structural & Mavridis, Roy \par (MIT MediaLab) & & & \cite{Mavridis2006} \\
Ke Jia Project & Formal & Chen et al. \par (Univ. of Science and Technology of China) & ASP (Answer Set Programming) & ASP & \cite{Chen2010} \\
{\sc KnowRob} & Formal & Tenorth, Beetz \par (TU Munich) & {\sc Prolog} & {\sc Prolog} + OWL-DL &  \cite{Tenorth2009a} \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & NKRL & & \cite{Sabri2011} \\
%OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
ORO & Formal & Lemaignan, Alami \par (LAAS-CNRS) & {\sc Java} & OWL-DL ({\sc Jena}) + {\sc Pellet} & \cite{Lemaignan2010} \\
OUR-K/OMRKF & Formal & Lim, Suh et al. \par (Hanyang Univ.) & ? & DL + Horn Clauses &  \cite{Lim2011, Suh2007} \\
PEIS KR\&R & Formal & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & \cite{Daoutis2009} \\
%Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

CAS (\emph{CoSy Architecture Schema}) Toolkit~\cite{Hawes2007} is a
comprehensive toolkit aimed at building cognitive architectures for robots
through a set of interconnected \emph{SA} (\emph{subarchitectures}). The CAS
does not expose a central knowledge base as seen in other works. It represents
instead knowledge as unrooted \emph{proxies}. Those proxies are formally
defined in \cite{jacobsson2008crossmodal} as $p= \langle F_p, u_p \rangle$ where $F_p$ is
a set of instantiated features (like $\phi^{Colour}_{red}$) and $u_p$ a
\emph{proxies union} that form an equivalence class corresponding to one
entity.

@@

@@

@@

Learning at the level of the knowledge representation system has been explored
in conjunction with visual perception systems (mentioned for instance, in the
CAST project, in~\cite{jacobsson2008crossmodal}). {\sc KnowRob}, by filling its pool of
facts from informations automatically extracted from the Web~\cite{Nyga2009},
can also be considered as a \emph{learning} system (it autonomously acquire
knowledge). We lack however a formal study of learning strategies and
techniques at the knowledge representation level.
